\documentclass[11pt,a4paper]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{fancyhdr}

\geometry{
  left=2.5cm,
  right=2.5cm,
  top=3cm,
  bottom=3cm
}

\title{
  GRA-Health-Swarm: \\
  Swarm Subjectivity for Health, Rejuvenation and Stress Resilience \\
  via Anokhin's Functional Systems and GRA Nullification
}
\author{oleg bits (qqewq)}
\date{\today}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\begin{document}

\maketitle

\begin{abstract}
This paper presents a mechanism for cybernetic modeling of \textbf{health, stress and disease} through P.K. Anokhin's Theory of Functional Systems combined with GRA-nullification.
The \texttt{GRA-Health-Swarm} repository implements this mechanism in software.

Key idea:
\begin{itemize}
  \item \textbf{Disease} = prolonged mismatch between the brain's prediction (Acceptor of Action Result -- AAR) and reality.
  \item In GRA terms: disease = chronically high foam $\Phi_{\text{total}} \gg 0$.
  \item \textbf{Health} = regime $\Phi_{\text{total}} \to 0$ via GRA-reset at the swarm level.
\end{itemize}

A swarm of agents models functional subsystems of the organism (stress, goals, body, environment, threats).
The \textbf{N\textsubscript{health}} operator (GRA-reset adapted for health) reconfigures goals, expectations and interactions, striving for a coherent state.

Scenarios:
\begin{itemize}
  \item \texttt{drone\_phobia/} -- constant fear of Ukrainian drones, chronic mismatch.
  \item \texttt{burnout/} -- work/war burnout.
  \item \texttt{rejuvenation/} -- rejuvenation and longevity.
  \item \texttt{chronic\_disease/} -- progression of chronic disease.
\end{itemize}

Rejuvenation theorem: if a biological swarm has at least one agent with a correct AAR (prediction of healthy state) and the N\textsubscript{health} operator is applied iteratively, then $\Phi_{\text{total}} \to 0$ is achievable.

This is \textbf{not a medical tool}, but a cybernetic model: a system can survive war without internal collapse.
\end{abstract}

\section{Introduction}

In modern approaches to health and stress, often individual aspects are considered: medicine, psychology, physiology.
Within the GRA (Gradient Reduction of Argumentative Foam) theory and Anokhin's Theory of Functional Systems, the notion of \textbf{foam} $\Phi$ is introduced as a measure of internal uncertainty, contradictoriness and mismatch.

Academician P.K. Anokhin showed that:
\begin{enumerate}
  \item The brain builds a \textbf{prediction of the result} (Acceptor of Action Result -- AAR).
  \item If reality \textbf{matches} the prediction -- stability, no stress.
  \item If reality \textbf{does not match} and the mismatch persists -- \textbf{chronic stress $\to$ disease}.
\end{enumerate}

This work proposes a mechanism where a swarm of agents (functional systems) can maintain itself in a state of \textbf{health} through foam $\Phi$ nullification, even under war, drone attacks and chronic stress.

\section{Theoretical Foundation}

\subsection{Anokhin's Theory of Functional Systems}

\begin{definition}
A \textbf{functional system} is an organization of activity of elements of different anatomical membership, directed towards achieving a useful adaptive result [Anokhin].
\end{definition}

Key components:
\begin{itemize}
  \item \textbf{Afferent synthesis} -- gathering information from the environment.
  \item \textbf{Dominant} -- main goal.
  \item \textbf{Acceptor of Action Result (AAR)} -- prediction of future result.
  \item \textbf{Efferent action} -- motor / physiological output.
  \item \textbf{Reverse afferentation} -- feedback from body and environment.
  \item \textbf{Result -- mismatch} -- error signal when prediction and reality do not match.
\end{itemize}

\subsection{GRA and Foam}

In GRA theory:

\begin{definition}
\textbf{Foam} $\Phi$ of an agent is a measure of internal contradictoriness of its argumentative space. High $\Phi$ corresponds to uncertainty, blurriness of goals and internal instability.
\end{definition}

\begin{definition}
\textbf{Health} $\approx$ low $\Phi_{\text{total}}$ (coherent functional system).
\end{definition}

\begin{definition}
\textbf{Disease / burnout / drone-phobia} $\approx$ chronically high $\Phi_{\text{total}}$ (chronic mismatch).
\end{definition}

\subsection{The Anokhin--GRA Bridge}

\begin{table}[h]
\centering
\caption{Mapping Anokhin's components to GRA}
\begin{tabular}{ll}
\toprule
\textbf{Anokhin} & \textbf{GRA} \\
\midrule
AAR (result prediction) & Agent's world model $\Psi$ \\
Reality & Data from environment \\
Mismatch & Foam $\Phi > 0$ \\
Chronic mismatch & Prolonged high $\Phi$ \\
Stress & System instability \\
Disease & System ``sick'' = $\Phi$ not minimized \\
Recovery & GRA-reset: operator $N \to \Phi \to 0$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{theorem}[Disease and Health in GRA]
\textbf{Disease} = prolonged mismatch between brain's prediction and reality. \\
\textbf{Healing} = swarm-level GRA-reset pushing $\Phi_{\text{total}} \to 0$.
\end{theorem}

\section{GRA-Reset for Health}

\subsection{The N\textsubscript{health} Operator}

The \textbf{N\textsubscript{health}} operator (GRA-reset adapted for health):
\begin{enumerate}
  \item Computes local foam $\Phi_i$ of each agent (stress, body, goals, environment).
  \item Detects high-foam configurations (chronic mismatch).
  \item Reconfigures goals, expectations and interactions:
  \begin{itemize}
    \item Adjusts unrealistic predictions (AAR recalibration).
    \item Strengthens feedback loops (reverse afferentation).
    \item Reduces contradictory goals between agents.
    \item Activates compensatory functional systems.
  \end{itemize}
  \item Strives for $\Phi_{\text{total}} \to 0$.
\end{enumerate}

\begin{theorem}[Rejuvenation Theorem]
If a biological swarm has at least one agent with a correct AAR (prediction of healthy state) and the N\textsubscript{health} operator is applied iteratively, then $\Phi_{\text{total}} \to 0$ is achievable, corresponding to a state of optimal health and rejuvenation.
\end{theorem}

\section{Implementation}

The \texttt{GRA-Health-Swarm} repository implements the described mechanism:

\begin{itemize}
  \item \texttt{core/} -- agents (stress, body, goals, environment), N\textsubscript{health} operator, interaction graph.
  \item \texttt{scenarios/} -- demonstration runs:
  \begin{itemize}
    \item \texttt{drone\_phobia/} -- constant fear of Ukrainian drones.
    \item \texttt{burnout/} -- work/war burnout.
    \item \texttt{rejuvenation/} -- rejuvenation and longevity.
    \item \texttt{chronic\_disease/} -- progression of chronic disease.
  \end{itemize}
  \item \texttt{math/} -- formal description of the theory.
  \item \texttt{paper/} -- this paper.
\end{itemize}

\section{Scenario: Drone-Phobia}

\textbf{Prediction}: ``I am safe, I am at home, there are no threats''. \\
\textbf{Reality}: constant drone attacks, explosions, alarms, sirens [BBC, New Izvestia]. \\
\textbf{Mismatch} $\to$ stress $\to$ drone-phobia.

In GRA:
\begin{itemize}
  \item Agent ``threat'' $\to$ high $\Phi$.
  \item Agent ``safety'' $\to$ low $\Phi$ only when there is shelter.
  \item $\Phi_{\text{total}}$ remains high $\to$ system ``sick''.
\end{itemize}

\textbf{What can be done}:
\begin{itemize}
  \item Reduce actual threat (fewer drones).
  \item Increase shelter availability.
  \item Reduce unpredictability (warnings, signals).
  \item Change environment (safe zones).
\end{itemize}

Operator N\textsubscript{health} does not stop war, but helps \textbf{not to lose one's mind in it}.

\section{Discussion}

The proposed mechanism shows that:
\begin{itemize}
  \item Disease can be modeled as chronically high foam $\Phi$.
  \item Health is the regime $\Phi_{\text{total}} \to 0$ via GRA-reset.
  \item ``Healing'' is not ``imagine yourself healthy'', but structural reorganization of a multi-agent functional system.
  \item This is \textbf{not a medical tool}, but a cybernetic model.
  \item A system can survive war without internal collapse if $\Phi_{\text{total}} \approx 0$ is maintained.
\end{itemize}

Future work:
\begin{itemize}
  \item Formalize the Rejuvenation Theorem in rigorous mathematical form.
  \item Investigate health stability against disruption of links in the swarm.
  \item Test the mechanism on real multi-agent systems.
\end{itemize}

\section{Connection to GRA Ecosystem}

\begin{itemize}
  \item \texttt{GRA-Multiverse-Final} -- universal operator $N$ ($\Phi \to 0$).
  \item \texttt{GRA-Swarm-Subject} -- subjectivity contagion in swarm.
  \item \texttt{GRA-Health-Swarm} -- specialization on health: ``subject'' = healthy organism, ``swarm'' = its functional systems.
\end{itemize}

\section*{Important Disclaimer}

\textbf{This repository is NOT a medical tool}. It is a cybernetic model of health, stress and resilience:
\begin{itemize}
  \item It \textbf{does not stop wars} or eliminate drones.
  \item It \textbf{does not replace medical treatment}.
  \item It \textbf{explains the mechanism}: why chronic mismatch causes disease and how structural reorganization can restore coherence.
\end{itemize}

\section*{Acknowledgments}

Academician \textbf{P.K. Anokhin} -- for the Theory of Functional Systems. \\
\textbf{K.V. Anokhin} -- for continuing and developing the legacy. \\
\textbf{GRA community} -- for building the nullification ecosystem.

\section*{License}

The project code is released under the MIT License. The full license text is included in the \texttt{LICENSE.txt} file of the repository.

\end{document}